Appendix S1: Supporting Information

### 2021-09-07 ms/SI.Rmd
Update SI and data readme

**`r s_table("moran")`**. Spatial autocorrelation in biodiversity metrics (richness, SES of PD, SES of FD, SES of RPD, SES of RFD) and independent variables (environmental variables and % apomictic taxa) as measured with Moran's *I*. Significant *I* > 0 indicates autocorrelation.

>>>>

**`r s_table("moran")`**. Spatial autocorrelation in biodiversity metrics (richness, SES of PD, SES of RPD, SES of FD, SES of RFD) and independent variables (environmental variables and % apomictic taxa) as measured with Moran's *I*. Significant *I* > 0 indicates autocorrelation.

### 2021-09-07 ms/data_readme.Rmd
Update SI and data readme

- ftol_data_release_v0.0.1.zip: Fern Tree of Life project global DNA alignment and phylogenetic tree 
- japan_climate.gpkg: Climate data in Japan downloaded from WorldClim database
- japan_deer_range.gpkg: Distribution maps of Japanese deer (Cervus nippon) in Japan
- japan_ferns_comm_full.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_inext_results.csv: Results of collection curve analysis on fern specimens in Japan
- japan_ferns_occ_summary.csv: Summary of specimen data of native, non-hybrid ferns in Japan
- japan_ferns_redundancy_by_res: Taxonomic richness, abundance, and redunancy at different spatial resolutions for native, non-hybrid ferns of Japan
- japan_ferns_shape_full.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_traits_lucid.csv: Morphological trait data of native, non-hybrid ferns in Japan
- japan_map_points.csv: Latitude and longitude of points used to produce a labeled map of Japan
- japan_map.gpkg: Map of Japan
- japan_protected_areas.gpkg: Protected areas in Japan
- testo_sundue_2016_calibrations.csv: Fossil calibration points used for phylogenetic dating analysis
- results.zip: Selected analysis results. Files include:
  - japan_ferns_biodiv.csv: Biodiversity statistics of native, non-hybrid ferns in Japan
  - japan_ferns_comm.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_shape.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_traits.csv: Trait matrix of native, non-hybrid ferns in Japan used for functional biodiversity analysis
  - japan_ferns_tree_dated.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs collapsed to polytomies
  - japan_ferns_tree_uncollapsed.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs not collapsed
  - japan_ferns_tree.tre: Maximim-likelihood phylogeny of native, non-hybrid ferns in Japan

@@

@@

2021-09-06

>>>>

- _targets.tar.gz: Tarball (compressed folder) including all workflow results produced by R targets package
- ftol_data_release_v0.0.1.zip: Fern Tree of Life project global DNA alignment and phylogenetic tree 
- japan_climate.gpkg: Climate data in Japan downloaded from WorldClim database
- japan_deer_range.gpkg: Distribution maps of Japanese deer (Cervus nippon) in Japan
- japan_ferns_comm_full.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_inext_results.csv: Results of collection curve analysis on fern specimens in Japan
- japan_ferns_occ_summary.csv: Summary of specimen data of native, non-hybrid ferns in Japan
- japan_ferns_redundancy_by_res: Taxonomic richness, abundance, and redunancy at different spatial resolutions for native, non-hybrid ferns of Japan
- japan_ferns_shape_full.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_traits_lucid.csv: Morphological trait data of native, non-hybrid ferns in Japan
- japan_map_points.csv: Latitude and longitude of points used to produce a labeled map of Japan
- japan_map.gpkg: Map of Japan
- japan_protected_areas.gpkg: Protected areas in Japan
- testo_sundue_2016_calibrations.csv: Fossil calibration points used for phylogenetic dating analysis
- results.zip: Selected analysis results. Files include:
  - japan_ferns_biodiv.csv: Biodiversity statistics of native, non-hybrid ferns in Japan
  - japan_ferns_comm.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_shape.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_traits.csv: Trait matrix of native, non-hybrid ferns in Japan used for functional biodiversity analysis
  - japan_ferns_tree_dated.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs collapsed to polytomies
  - japan_ferns_tree_uncollapsed.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs not collapsed
  - japan_ferns_tree.tre: Maximim-likelihood phylogeny of native, non-hybrid ferns in Japan

@@

_targets.tar.gz: Tarball (compressed folder) including all workflow results
produced by R targets package. This is provided to enable inspection of workflow
steps without running the entire workflow from the beginning. To use it, unpack
the tar achive with the command "tar -xzf _targets.tar.gz". Then, in R, the
"tar_load()" function in the R package "targets" can be used to load any
workflow step (target) defined in _targets.R
(https://github.com/joelnitta/japan_ferns_spatial_phy/blob/main/_targets.R). For
more information on the structure of the _targets folder and how to use it, see
https://github.com/ropensci/targets.

MD5 checksum: FIXME (add manually, since this can't be calculated from inside the targets workflow)

@@

2021-09-07
